---
title: "EDAV Fall 2019 Final Project"
author: Lin Jiang, Han Xu and Shuo Yang
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
  beamer_presentation:
    fig_width: 6
    toc: yes
urlcolor: blue
---



```{r,echo=FALSE,message=FALSE}
options("digits" = 5)
options("digits.secs" = 3)
 
```

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE, fig.align='center')
```

```{r load packages, include=FALSE}
library(tidyverse)
library(ggplot2)
library(parcoords)
library(ggplot2)
library(ggmap)
library(viridis)
library(GGally)

```
# Introdution

Airbnb, . 

Airbnb not only has changed the possibilites of travel and ways of living, but also 
brought new business potetials. We are interested in exploring the data generated from
Airbnb, analyzing the data to find interesting facts about airbnb listing in New York.
We hope we could generate some useful insights to provide guidances for
customers and business suggestions for hosts. 


# Get and Prepare Data

Data source: http://insideairbnb.com/get-the-data.html.

The data source provides a dataset of information from airbnb. We use the most 
recent (Sep, 2019) dataset for New York. The data is not cleaned, so we need to 
spend some time to tidy it. 

The first obstacle is that the data file is relatively large. The csv. file 
downlowded is more than 180MB. So we just select the columns relavent to our analysis.
We also exclude lists that without reviews, as we want to focus on. 

【Another obstacle is that some information is compressed into one cell, like amenities.
Amenities compress all the amenities provided in to one lone string, and it is
not seperated by simple delimiter. We have tried to transform amenities into a 
seperate tidy data frame. We will try to clean other similar columns.】（不用的话可以删了）


Additionally, we define an active list as the onces received reviews within the past 12 months.
Also we only includes data having price larger than zero, since we found that occurence of zero in price 
may due to error in data colleting. 

For the cleaning fee (`cleaning_fee`) and security deposit (`security_deposit`), 
it is intuitive to replace the missings by 0. There are small amount of other variables 
are missing, we simply exclude the listings. It might be also due to collection
error of the original data.

Finally, there are 28098 listings and 62 variables for our analysis. We are interested in
a few areas including Price, Reviews, Room Type, Host Response Rate, etc.
Our analysis answered some interesting questions about Airbnb listings. 



**amentities for backup**


```{r amenities, eval = FALSE}
#split amenities into tidy data frame
##function to modify amenities string
split_amenities<-function(x){
  #x is an input string
  x<-str_replace_all(x,"[{}]",",") #remove {}
  temp<-str_split(x,"\\\"")[[1]] #split by \"
  temp[str_starts(temp,"[,]") | str_ends(temp,"[,]")]<-str_replace_all(temp[str_starts(temp,"[,]") | str_ends(temp,"[,]")],"[,]","|")
  temp<-str_remove(temp,"^\\|")
  temp<-str_remove(temp,"\\|$")
  temp<-temp[temp!=""]
  out<-paste(temp,collapse = "|")
  return(out)
}

#38 list has no amenities
dat2<-dat1%>%select(id, amenities)%>%
  rowwise()%>%
  mutate(amenity = split_amenities(amenities))
dat3<-dat2%>%separate_rows(amenity,sep="\\|")

##output amenities
#write_csv(dat3%>%select(-amenities),"./data/amenities_201909.csv")
```


# Analysis
```{r include = FALSE, message = FALSE, warning = FALSE}
airbnb_cleaned <- read_csv("data_cleaned.csv")
```

The majority of listings in our data are among Manhattan and Brooklyn. The closer to the new york city downtown area, the denser the listings. 
```{r echo = FALSE}
## map for listings
data = airbnb_cleaned
data_map_all <- data %>% dplyr::select(id, longitude, latitude)
sbbox <- make_bbox(lon = data_map_all$longitude, lat = data_map_all$latitude, f = .001)

ny_map_all <- get_map(location = sbbox, maptype = "satellite", source = "google")
ggmap(ny_map_all) + 
  geom_point(data = data_map_all, mapping = aes(x = longitude, y = latitude), color = "red", size = 0.0011, alpha = 0.6)

```



## Price
Booking price is always an important factor both customers and hosts care about.
In this section, we want to explore the facts of airbnb booking price in the market of New York. 


### How's Booking Price Distributed?

```{r echo=FALSE, message = FALSE, warning = FALSE}
#Distribution of Price in total
ggplot(data = airbnb_cleaned, aes(x = price)) +
  geom_histogram(bins = 20, aes(y = ..density..), fill = "lightblue") + geom_density()+
  ggtitle("Distribution of Price")
  
  
```


```{r echo=FALSE, message = FALSE, warning = FALSE}
#Distribution of Price in total
ggplot(data = airbnb_cleaned, aes(x = price)) +
  geom_histogram(bins = 20, aes(y = ..density..), fill = "lightblue") + geom_density()+
  scale_x_log10() +
  ggtitle("Distribution of Price (transformed)") +
  geom_vline(xintercept = round(median(airbnb_cleaned$price), 2), size = 1, color = 'red') 
```

The first plot is a general plot of distribution of price, we could see that it is 
skewed right with very long tail. Thus, we do a log 10 transformation so that we 
could have better visualization. The distribution shows that the median of price 
is 100. 

The boxplot in the following also shows that most of the listings have a price
under 200 dollars. There are some listings have ridiculous high prices. 
What are these listings? Why are they so expensive?
Let's further explore these lisitngs with high prices. 


```{r echo=FALSE, message = FALSE, warning = FALSE}
#boxplot of price

ggplot() + geom_boxplot(data = airbnb_cleaned, aes(x = "price", y = price))+
  ggtitle("Boxplot of Price") +
  scale_y_continuous(breaks = c(0, 100, 200, 300,400,500,600,700,800,900,1000)) +
  coord_flip()


```

### What Makes Some Listings Most Expensive?



```{r echo = FALSE, fig.width= 10}
high_price <- airbnb_cleaned %>%
  filter(price > 600)


require(gridExtra)

plot1 <- high_price %>%
  group_by(neighbourhood_group_cleansed) %>%
  summarise(counts = n()) %>%
  arrange(desc(counts))%>%
  
  
  ggplot() + geom_bar(aes(x = reorder(neighbourhood_group_cleansed, counts), y = counts), 
                      stat = 'identity', fill = '#3CA9FC') + xlab("neighbourhood") + ggtitle('Neighbourhood counts of listing with 600+ price')



plot2 <- high_price %>%
  group_by(neighbourhood_cleansed) %>%
  summarise(counts = n())%>%
  arrange(desc(counts)) %>%
  filter(counts > 8) %>%
 ggplot() + geom_bar(aes(x = reorder(neighbourhood_cleansed, counts), y = counts), 
                      stat = 'identity', fill = '#3CA9FC') + xlab("neighbourhood") + 
  coord_flip() + ggtitle('Deatails of Neighbourhood')

grid.arrange(plot1, plot2, ncol=2)
```
We foucus on the listings with price more than $600. We could see that most of the
listings belongs to Manhattan area, which is reasonable. Futhermore, most of the listings 
with high price are in Midtown, which is also not unexpected, because Midtown is 
the central portion of Manhattan.



```{r, echo = FALSE, fig.width= 10}
plot1 <- high_price %>%
  group_by(room_type) %>%
  summarise(counts = n())%>%
  arrange(desc(counts)) %>%
  ggplot() + geom_bar(aes(x = reorder(room_type, counts), y = counts), 
                      stat = 'identity',  fill = '#3CA9FC') + xlab("room_type") + 
  coord_flip() + ggtitle('Room type ') 


plot2 <- high_price %>%
  group_by(bedrooms) %>%
  summarise(counts = n()) %>%
  arrange(desc(counts)) %>% 
    ggplot() + geom_bar(aes(x = reorder(bedrooms, counts), y = counts), 
                      stat = 'identity',fill = '#3CA9FC') + xlab('number of bedrooms')+
  coord_flip() + ggtitle('Number of bedrooms ') 
  

grid.arrange(plot1, plot2, ncol=2)
```

Moreover, we find the room type of most of these listings with high price is entire
home/apt and the number of bedrooms are about 2-4. This result may explain the high
price of these listings. Booking a big apratment in Midtown of Manhattan is reasonable to 
be expensive. 




### Does Location Make a Difference?
Based on the price distribution above, we are interested in how prices are affected by different locations. We plotted the below push pin map which shows the price distribution among new york districts. 
```{r echo = FALSE}
## map for different price
ny_price <- data %>% mutate(price_group = 
         case_when(price <= 100 ~ '$100', 
                   price <= 250 ~ '$100-$250',
                   price <= 500 ~ '$250-$500',
                   TRUE ~ '>$500')) 
ny_price$price_group <- factor(ny_price$price_group, levels = c('$100',  '$100-$250', '$250-$500', '>$500'))

data_map_price <- ny_price %>% select(id, longitude, latitude, price_group)
sbbox3 <- make_bbox(lon = data_map_price$longitude, lat = data_map_price$latitude, f = .001)

ny_map_price <- get_map(location = sbbox3, maptype = "satellite", source = "google")
ggmap(ny_map_price) + 
  geom_point(data = data_map_price, mapping = aes(x = longitude, y = latitude, color = price_group), size = 1, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2")


```
Most of the listings are among $100-$250 per night and the closer we are to new york downtown, the higher the price. The purple points indicate expensive listings above $250 per night. We can rarely see listings that cost more than $500 per night.



Indeed, price is largely affected by location. To better illustrate, we plotted the average price per night for the five neighborhoods and we can see that Bronx, Staten Island, Queens are almost the same. Brooklyn and Manhattan are more expensice by about $50 to $100 per night, which is a large amount considering our majority of the prices are around $100 per night. 

```{r echo = FALSE}
#average price for different area
avg_airbnb <- airbnb_cleaned %>%
  group_by(neighbourhood_group_cleansed) %>%
  summarize(avg_price = mean(price)) %>%
  arrange(desc(avg_price))
colnames(avg_airbnb) <- c("neighbourhood","avg_price" )

  
ggplot(avg_airbnb) + 
  geom_bar(aes(x = reorder(neighbourhood, avg_price), y = avg_price),stat="identity", fill = '#3CA9FC') +
  xlab("Neighbourhood") +
  ggtitle("Average price for different area ")

```

```{r echo = FALSE}
#Price distribution of different neighborhood 
ggplot(airbnb_cleaned, aes(x= price, color = neighbourhood_group_cleansed)) + geom_density() +
   scale_x_log10() +
  ggtitle("Price distribution in different neighbourhoods (transformed)")+
  scale_color_brewer(palette = "Dark2")

```


### Are Deposite and Clearning Fee Proportional to Price?



### Does Room Type Affect Price?
Room type is also an important factor customers care about. 
There are four room types in Airbnb market: entire home/apt, private room, 
shared room, and hotel room.


```{r echo = FALSE}
#Price distribution of different room type
ggplot(airbnb_cleaned, aes(x= price, color = room_type)) + geom_density() +
   scale_x_log10() +
  ggtitle("Price distribution of different room type (transformed)") + scale_color_brewer(palette = "Dark2")

```

First, we take a look at the price distribution for different room type. We could 
see that entire home/apt and hotel/room have realative higher price than private room 
and shared room, which is reasonable. Additionally, shared room has realtive lowest price in the 
market. These findings does not violate our common sense. We continue exploring the price distribution 
for different room type in four neighbourhoods.


```{r echo = FALSE}
avg_airbnb <- airbnb_cleaned %>%
  group_by(neighbourhood_group_cleansed, room_type) %>%
  summarize(avg_price = mean(price)) %>%
  arrange(neighbourhood_group_cleansed) 

ggplot(avg_airbnb, aes(x = reorder(neighbourhood_group_cleansed, avg_price), y = avg_price, fill = room_type)) + 
  geom_bar(stat="identity",position = "dodge") + ggtitle("Average price for different neighborhoods with room type")+
  xlab("neighbourhood") + scale_color_brewer(palette = "Dark2")

```
From the graph, we could find that in Manhattan, hotel room has the highest average price. 
Also, we could see that entire room/apt always much higher than private room and shared
room. The price for entire room/apt is relatively very high in Manhattan. 
Therefore, if customers has limited budgets, it is not wise to look for hotels and entire home/apt 
in Manhattan. 
For shared room, Brooklyn and Bronx has the lowest average price.
For entire home/apt and private room, Staten Island has the lowest average price. 




```{r echo=FALSE, message = FALSE, warning = FALSE}
## map for different room types
data_map_room <- data[sample(nrow(data)),] %>% select(id, longitude, latitude, room_type)
sbbox1 <- make_bbox(lon = data_map_room$longitude, lat = data_map_room$latitude, f = .001)

ny_map_room <- get_map(location = sbbox1, maptype = "satellite", source = "google")
ggmap(ny_map_room) + 
  geom_point(data = data_map_room, mapping = aes(x = longitude, y = latitude, color = room_type), size = 1, alpha = 0.5) + 
  scale_fill_brewer(palette = "Dark2")
```

Surprisingly, at such an expensive living area like Manhattan, lots of listings 
are "Entire Home/Apt". It's true that Manhattan has the most expensive listings 
but they actually also have relative good qualities (instead of being all
shared rooms and small private rooms).




### Does Property Type Affect Price?


```{r echo = FALSE, message = FALSE, warning = FALSE}
temp <- dplyr::summarise(group_by(airbnb_cleaned, property_type, neighbourhood_group_cleansed), freq = n())  %>% filter(freq > 70)

df2 <- temp %>%
group_by(neighbourhood_group_cleansed) %>%
mutate(prop = freq/sum(freq)) %>%
ungroup()

ggplot(df2,
aes(x = neighbourhood_group_cleansed, y = prop, fill = property_type)) +
geom_bar(stat = "identity") + labs(x = "Neighborhood",
y = "Proportion",
title = "Neighborhood by Property Type") +
theme(legend.title = element_blank()) + 
  scale_fill_brewer(palette = "Dark2")

```



```{r echo = FALSE}
## map for different property type
data_map_property <- data[sample(nrow(data)),] %>% filter(property_type %in% c('Apartment', 'House', 'Townhouse', 'Condominium', 'Loft','Guest suite', 'Serviced apartment', 'Hotel')) %>% select(id, longitude, latitude, property_type)
sbbox2 <- make_bbox(lon = data_map_property$longitude, lat = data_map_property$latitude, f = .001)

ny_map_property <- get_map(location = sbbox2, maptype = "satellite", source = "google")
ggmap(ny_map_property) + 
  geom_point(data = data_map_property, mapping = aes(x = longitude, y = latitude, color = property_type), size = 1, alpha = 0.5) + 
  scale_fill_brewer(palette = "Dark2")

```




### What's the correlation between price and other variables
There are other variables may be important factors that affects price, such as 
number of reveiws, number of minimum night, host response rate, and review scores rating.
However, from the pairwise scatter plot, we could see that price actually does not 
have strong correlation with these variables. 
The price is set by hosts and not every host have multiple financial and marketing information.
Additionally, not all the host's purpose is making money, so price may not reflect actual market values.
Price setting is individual subjective. 
Therefore, we could see that a high price does not guarantee a good services. 


```{r echo=FALSE, message = FALSE, warning = FALSE}
#price vs number_of_reveiws, minimum_night, host_response_rate, review_scores_rating
pairPlot <- airbnb_cleaned[,c("price", "number_of_reviews", "minimum_nights", "host_response_rate", "review_scores_rating") ]
ggpairs(pairPlot)

```



## Reviews
### What's the most important variables that affects customers' review

Analyzing reviews can provide customers' opinions of valuaing the quality of airbnb
services. Customers can rate an Airbnb stay in six aspects: cleanliness, accuracy, 
checking, communication, location, and value which represent an overall feeling of the stay. 
It is useful to explore what aspect affects the "value rating" the most. Knowing
customers' cares can help hosts to understand how to provide better service and 
get better rating results. 


```{r echo = FALSE,  message = FALSE, warning = FALSE, fig.width= 15}
dat_review<- airbnb_cleaned%>%
  dplyr::select(starts_with("review"))%>%
  dplyr::select(2:7)

colnames(dat_review)<-gsub("review_scores_","",colnames(dat_review))
dat_review<-dat_review%>%
  gather(key=others,value="scores",-value)

plot1 <- ggplot(dat_review)+
  geom_bar(aes(x=fct_reorder(others,scores==10,sum),
               fill=others,alpha=scores==10),position='fill')+
  coord_flip()+
  scale_alpha_discrete(range=c(0.5,1))+
  scale_fill_brewer(palette = "Dark2")+
  labs(y="",x="",
       title="Percentage of 10 in Review Scores",
       alpha="Score of 10",
       fill="Review Score")+
  theme(axis.text.x =element_text(size=19),
         axis.text.y=element_text(size=15),
        axis.title=element_text(size=14,face="bold"))



 
plot2<- ggplot(dat_review%>%filter(scores==10)%>%
         group_by(others,value==10)%>%
         dplyr::summarise(n=sum(value))%>%
         ungroup()%>%group_by(others)%>%
         mutate(perc=n/sum(n))%>%
         ungroup()%>%mutate(value=`value == 10`))+
  geom_bar(aes(x=fct_reorder(others,perc,max),y=perc,
               fill=others,
               alpha=value),
           position='fill',
           stat="identity")+
  coord_flip()+
  scale_alpha_discrete(range=c(0.5,1))+
  scale_fill_brewer(palette = "Dark2")+
  labs(y="",x="",
       title="Percentage of 10 in Review of Value for Other 10-score Reviews",
       alpha="Score of 10\nin Value",
       fill="Review Score") +
  theme(axis.text.x=element_text(size=19),
        axis.text.y=element_text(size=15),
        axis.title=element_text(size=14,face="bold"))

grid.arrange(plot1, plot2, ncol=2)
```

From the graph on the left side, we could see the the percentage of full point for
each reviews of different aspects. Customers tend not to give full point to cleanliness score.
From the graph on the right side, we could see that for each aspects, among the listing received
full point in the specific aspects, what is the percentage that the review of value
is also full point. Cleanliness has the highest percentage which reflects that if people 
give full point to cleaning, they may have more tendency to give full point to the reveiw of 
value. In addition, accuracy has the second highest percentage. Thus, this result
may imply that cleaning and accuracy are the most important factor that affect
customers' assessement of the value of the stay.

Therefore, we conclude that hosts should pay attention to cleaning of their rooms 
and they should not give exaggerated descriptions to their listings. 

## Amenities
###
## Interactive



# Conclusion
From this analysis, we 



# Appendix: code

```{r Data Importing and Cleaning, eval = FALSE}
#Data Importing and Cleaning
data <- read_csv ("listings_201909.csv", na=c("","NA","N/A"))

##select columns
dat<-data%>%
  select(-c(scrape_id:xl_picture_url))%>%
  select(-host_url, -host_name, -host_location, -host_about,
         -host_acceptance_rate, -host_thumbnail_url, -host_picture_url, 
         -host_neighbourhood)%>%
  select(-street,-city,-state, -market, -smart_location, -country, 
         -country_code)%>%
  select(-jurisdiction_names, -license,-weekly_price,-monthly_price, 
         -square_feet)%>%
  select(-c(calendar_updated:calendar_last_scraped)) 
#dim(dat)  #48377    62

##modify data type
dat<-dat%>%
  mutate_at(c("host_response_rate","extra_people",
              "price","security_deposit","cleaning_fee"),
            str_remove_all,pattern="[%$]")%>%
  mutate_at(c("host_response_rate","extra_people",
              "price","security_deposit","cleaning_fee"),
            as.numeric)

##select lists which have reviews within the last 12 months
data_cleaned<-dat%>%filter(!is.na(first_review))%>%
  filter(last_review>='2018-09-01')
#dim(dat1) #28105    62

#clean NA
##replace missing values
data_cleaned$cleaning_fee[is.na(data_cleaned$cleaning_fee)] <- 0
data_cleaned$security_deposit[is.na(data_cleaned$security_deposit)] <- 0
data_cleaned<-data_cleaned%>%filter(price>0)

##exclude missing values
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

data_cleaned <- completeFun(data_cleaned, c("review_scores_value", "review_scores_checkin", "review_scores_accuracy", "review_scores_communication", "review_scores_cleanliness","review_scores_rating","neighbourhood", "review_scores_location", "price", "bedrooms", "beds","bathrooms", "host_identity_verified","zipcode"))

#sort(colSums(is.na(data_cleaned)),decreasing = TRUE)

dim(data_cleaned) #28098

#cleaned data output
##write_csv(data_cleaned,"data_cleaned.csv")
```

#Get Amenities data
```{r amenities, eval = FALSE}
#split amenities into tidy data frame
##function to modify amenities string
split_amenities<-function(x){
  #x is an input string
  x<-str_replace_all(x,"[{}]",",") #remove {}
  temp<-str_split(x,"\\\"")[[1]] #split by \"
  temp[str_starts(temp,"[,]") | str_ends(temp,"[,]")]<-str_replace_all(temp[str_starts(temp,"[,]") | str_ends(temp,"[,]")],"[,]","|")
  temp<-str_remove(temp,"^\\|")
  temp<-str_remove(temp,"\\|$")
  temp<-temp[temp!=""]
  out<-paste(temp,collapse = "|")
  return(out)
}

#38 list has no amenities
dat2<-dat1%>%select(id, amenities)%>%
  rowwise()%>%
  mutate(amenity = split_amenities(amenities))
dat3<-dat2%>%separate_rows(amenity,sep="\\|")

##output amenities
#write_csv(dat3%>%select(-amenities),"./data/amenities_201909.csv")
```